
\chapter{Reference}%\addcontentsline{toc}{chapter}{Reference}
\begin{thebibliography}{10}

\bibitem{wiki}
Wikipedia. (n.d.). \textit{Blood donation}. Retrieved from \url{https://en.wikipedia.org/wiki/Blood_donation}

\bibitem{who}
World Health Organization. (2020). \textit{Blood safety and availability: Key facts}. Retrieved from \url{https://www.who.int/news-room/fact-sheets/detail/blood-safety-and-availability}

\bibitem{django-github}
Django Software Foundation. (2024). \textit{Django project}. Retrieved from \url{https://github.com/django/django}

\bibitem{postgres-docs}
PostgreSQL Global Development Group. (2024). \textit{PostgreSQL documentation}. Retrieved from \url{https://www.postgresql.org/docs/}

\bibitem{kumar2020}
Kumar, A., \& Gupta, S. (2020). Digital transformation in blood donor management: A comprehensive study. \textit{Journal of Healthcare Information Systems}, \textit{15}(3), 45–62.

\bibitem{sharma2019}
Sharma, R., Patel, M., \& Singh, K. (2019). Blood donor management systems in developing countries: Challenges and opportunities. \textit{International Journal of Medical Informatics}, \textit{128}, 89–97.

\bibitem{who2}
World Health Organization. (2020). \textit{Blood safety and availability: Key facts}. Retrieved from \url{https://www.who.int/news-room/fact-sheets/detail/blood-safety-and-availability}

\bibitem{django-docs}
Django Software Foundation. (2024). \textit{Django documentation}. Retrieved from \url{https://docs.djangoproject.com/}

\bibitem{postgresql}
PostgreSQL Global Development Group. (2024). \textit{PostgreSQL documentation}. Retrieved from \url{https://www.postgresql.org/docs/}

\bibitem{nrcs}
Nepal Red Cross Society. (2023). \textit{Blood donation services in Nepal: Annual report}. Kathmandu: NRCS Publications.

\end{thebibliography}
