\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[top=1in,bottom=1in,left=1.5in,right=1in,headheight=14.5pt]{geometry}

% --- Fonts and Spacing ---
\usepackage{newtxtext,newtxmath}  % Times New Roman–like with bold support
\usepackage{setspace}
\renewcommand{\contentsname}{Table of Contents}

% --- Bibliography ---
\usepackage[
    backend=biber,
    style=numeric-comp,
    citestyle=numeric-comp,
    sorting=none,
    maxcitenames=2
]{biblatex}
\addbibresource{ref.bib}

% --- Hyperlinks ---
\usepackage[hidelinks]{hyperref}

% --- Lists ---
\usepackage{enumitem}

% --- Tables ---
\usepackage{array}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}

% --- Graphics and Floats ---
\usepackage{graphicx}
\usepackage{float}

% --- Math and Symbols ---
\usepackage{amssymb}
\usepackage{amsmath}

% --- Colors ---
\usepackage{xcolor}
\definecolor{taskcolor}{named}{black}
\definecolor{lightgray}{gray}{0.95}

% --- Code Listings ---
\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

% --- Headers and Footers ---
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headheight}{14.5pt}

% --- Title formatting ---
\usepackage{titlesec}
\titleformat{\chapter}[display]{\centering\Large\bfseries}{\centering\chaptertitlename\ \thechapter}{1ex}{}
\titlespacing*{\chapter}{0ex}{-2ex}{4ex}

\fancypagestyle{plain}{
  \fancyhf{}
  \fancyfoot[C]{\thepage}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{2}
\hyphenation{Post-greSQL Django Health-Metrics Emer-gency-Request Blood-Inventory Sys-tem-Noti-fi-ca-tion}

% --- Document Starts ---
\begin{document}
\sloppy
\tolerance=2000
\emergencystretch=3em
\hbadness=10000

% --- Title Page ---
\include{title}
\thispagestyle{empty}

% --- Roman numbering for front matter ---
\cleardoublepage
\pagenumbering{roman}
\setcounter{page}{1}

% --- Bonafide Certificate ---
\include{bonafide}

% --- Acknowledgement ---
\chapter*{ACKNOWLEDGEMENT}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENT}

We are pleased to present the final defense report of our project titled "Blood Donor Information Management System", undertaken as a part of the curriculum of Bachelor of Computer Engineering at Khwopa Engineering College.
\\\\
We would like to express our sincere gratitude to all those who have supported us throughout the completion of this project. We are especially thankful to our respected Head of Department, Er. Bikash Chawal, and Deputy Head of Department, Er. Avijit Karn, for their continuous guidance, encouragement, and valuable feedback during the entire development process.
\\\\
Our heartfelt thanks go to Purbanchal University and Khwopa Engineering College, Bhaktapur, for providing us with this opportunity to work on a real-world oriented project that has significantly enhanced our technical, analytical, and project management skills.
\\\\
We also appreciate the cooperation and support of our supervisors, teachers, friends, and seniors who have offered constructive suggestions and moral support, which have been crucial to the successful completion of our work. Special thanks to Er. Anish Baral for providing valuable guidance and continuous support throughout the entire project lifecycle.
\\\\
We extend our gratitude to the administration and staff of Khwopa Engineering College for providing the necessary resources and infrastructure required for the successful implementation and deployment of this project.
\\\\
Finally, we are grateful to our families for their unwavering support and patience during the intensive development and documentation phases of this project.

\vspace{1cm}
\noindent
\textbf{With Regards,}\\[0.5cm]
\begin{tabular}{ll}
    Bishal Shrestha & (790310)\\
    Chirayu Shrestha & (790311)\\
    Pappu Yadav & (790324)\\
    Prashant Ghimire & (790328)
\end{tabular}

\pagebreak

% --- Abstract ---
\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}

The Blood Donor Information Management System (BDIMS) is a comprehensive web-based application designed to modernize and streamline blood donation management for healthcare institutions in Nepal. The system addresses critical challenges in donor information management, blood inventory tracking, and emergency response coordination through a centralized digital platform.
\\\\
Built using Django framework and PostgreSQL database, BDIMS provides role-based access for both administrators and donors. The system enables administrators to manage comprehensive donor databases, track real-time blood inventory across multiple centers, handle emergency blood requests, monitor donor eligibility with automated 56-day rule calculations, and generate detailed analytical reports. Donors can maintain detailed personal and medical profiles, track health metrics over time, view complete donation histories, update location information with interactive map integration, and respond to emergency blood requests.
\\\\
The system incorporates advanced features including interactive Leaflet.js-based maps for location tracking, automated eligibility verification, multi-channel notification system, health metrics monitoring, blood compatibility checking, and comprehensive reporting capabilities. Security is ensured through role-based authentication, password hashing, and session management.
\\\\
BDIMS successfully replaces traditional paper-based systems with an efficient, scalable digital solution that improves coordination between blood banks, hospitals, and donors. The system has been thoroughly tested and optimized for performance, achieving 100\% functionality for all core features including donor management, inventory tracking, emergency request handling, and analytical reporting.

\vspace{1em}
\noindent\textbf{Keywords:} \textit{Blood Donation Management, Django Framework, PostgreSQL Database, Emergency Response System, Donor Eligibility Tracking, Healthcare Information System, Interactive Maps, Location-Based Services}

\pagebreak

% --- Table of Contents ---
\tableofcontents
\pagebreak

% --- List of Figures ---
\listoffigures
\pagebreak

% --- List of Tables ---
\listoftables
\pagebreak

% --- List of Abbreviations ---
\chapter*{LIST OF ABBREVIATIONS}
\addcontentsline{toc}{chapter}{LIST OF ABBREVIATIONS}

\begin{table}[h]
    \begin{tabular}{l l}
        \textbf{Abbreviations} & \textbf{Meaning} \\
        API & Application Programming Interface\\
        BDIMS & Blood Donor Information Management System\\
        CSS & Cascading Style Sheets\\
        CSV & Comma-Separated Values\\
        CSRF & Cross-Site Request Forgery\\
        DB & Database\\
        DBMS & Database Management System\\
        DNS & Domain Name System\\
        ER & Entity Relationship\\
        FP & False Positive\\
        FN & False Negative\\
        GPS & Global Positioning System\\
        GUI & Graphical User Interface\\
        HoD & Head of Department\\
        HTML & HyperText Markup Language\\
        HTTP & HyperText Transfer Protocol\\
        HTTPS & HyperText Transfer Protocol Secure\\
        IDE & Integrated Development Environment\\
        IP & Internet Protocol\\
        JS & JavaScript\\
        JSON & JavaScript Object Notation\\
        KhEC & Khwopa Engineering College\\
        MVC & Model-View-Controller\\
        MVT & Model-View-Template\\
        NRCS & Nepal Red Cross Society\\
        ORM & Object-Relational Mapping\\
        OS & Operating System\\
        PDF & Portable Document Format\\
        SQL & Structured Query Language\\
        TN & True Negative\\
        TP & True Positive\\
        UI & User Interface\\
        URL & Uniform Resource Locator\\
        UX & User Experience\\
        VS Code & Visual Studio Code\\
        WHO & World Health Organization\\
    \end{tabular}
\end{table}
\pagebreak

% --- Start Main Content ---
\cleardoublepage
\pagenumbering{arabic}
\setcounter{page}{1}

% --- Chapters ---
\include{chapter_1_introduction}
\include{chapter_2_literature_review}
\include{chapter_3_project_management}
\include{chapter_4_methodology}
\include{chapter_5_requirement_analysis}
\include{chapter_6_system_design}
\include{chapter_7_implementation}
\include{chapter_8_testing_results}
\include{chapter_9_conclusion}

% --- Bibliography ---
\printbibliography[heading=bibintoc, title={REFERENCES}]

% --- Appendix ---
\renewcommand{\thesection}{\Alph{section}}
\include{appendix}
    
\end{document}
