\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[top=1in,bottom=1in,left=1.5in,right=1in]{geometry}

% Packages
\usepackage{graphicx}
\usepackage{float}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}

% Font and spacing
\onehalfspacing
\renewcommand{\contentsname}{TABLE OF CONTENTS}

% Bibliography
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\addbibresource{references.bib}

% Code listing style
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

% Headers and footers
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

% Chapter title formatting
\titleformat{\chapter}[display]
{\normalfont\Large\bfseries\centering}
{\chaptertitlename\ \thechapter}{20pt}{\Large}

\titlespacing*{\chapter}{0pt}{-20pt}{20pt}

% Document begins
\begin{document}

% Title page
\include{title}

% Front matter
\pagenumbering{roman}
\setcounter{page}{1}

% Bonafide Certificate
\include{bonafide}

% Acknowledgement
\chapter*{ACKNOWLEDGEMENT}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENT}

We are pleased to present the final defense report of our project titled \textbf{"Blood Donor Information Management System (BDIMS)"}, undertaken as a part of the curriculum of Bachelor of Computer Engineering at Khwopa Engineering College, Bhaktapur.

We would like to express our sincere gratitude to our respected Head of Department, \textbf{Er. Bikash Chawal}, and our project supervisor, \textbf{Er. Anish Baral}, for their continuous guidance, encouragement, and valuable feedback throughout the project development process.

Our heartfelt thanks go to Purbanchal University and Khwopa Engineering College for providing us with the opportunity and resources to work on this real-world healthcare management system that has significantly enhanced our technical and problem-solving skills.

We are grateful to all the teachers, staff members, and our friends who have offered constructive suggestions and moral support during the development and documentation phases of this project.

Finally, we thank our families for their unwavering support and patience throughout this academic journey.

\vspace{1cm}
\noindent
\textbf{Team Members:}\\[0.3cm]
\begin{tabular}{ll}
    Bishal Shrestha & (790310)\\
    Chirayu Shrestha & (790311)\\
    Pappu Yadav & (790324)\\
    Prashant Ghimire & (790328)
\end{tabular}

\newpage

% Abstract
\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}

The Blood Donor Information Management System (BDIMS) is a comprehensive web-based application developed to modernize blood donation management for healthcare institutions. The system addresses critical challenges in donor information management, blood inventory tracking, and emergency response coordination through a centralized digital platform.

Built using the Django web framework and PostgreSQL database, BDIMS provides role-based access for administrators and donors. The system enables efficient donor registration, health metrics tracking, donation history management, blood inventory monitoring, and emergency request handling. Key features include interactive location-based mapping using Leaflet.js, automated eligibility verification based on the 56-day donation interval rule, real-time blood inventory tracking, and emergency alert notifications.

The system successfully replaces manual paper-based processes with an efficient digital solution that improves coordination between blood banks, hospitals, and donors. Through comprehensive testing, the system demonstrates 100\% functionality for all core features including user authentication, donor management, inventory control, and emergency response.

\noindent\textbf{Keywords:} Blood Donation Management, Django Framework, PostgreSQL, Healthcare Information System, Emergency Response, Web Application

\newpage

% Table of Contents
\tableofcontents
\newpage

% List of Figures
\listoffigures
\newpage

% List of Tables
\listoftables
\newpage

% Abbreviations
\chapter*{LIST OF ABBREVIATIONS}
\addcontentsline{toc}{chapter}{LIST OF ABBREVIATIONS}

\begin{table}[h]
\begin{tabular}{ll}
\textbf{Abbreviation} & \textbf{Meaning} \\
\hline
API & Application Programming Interface \\
BDIMS & Blood Donor Information Management System \\
CSS & Cascading Style Sheets \\
CSRF & Cross-Site Request Forgery \\
DBMS & Database Management System \\
ER & Entity Relationship \\
HTML & HyperText Markup Language \\
HTTP & HyperText Transfer Protocol \\
HTTPS & HyperText Transfer Protocol Secure \\
IDE & Integrated Development Environment \\
JS & JavaScript \\
JSON & JavaScript Object Notation \\
MVC & Model-View-Controller \\
MVT & Model-View-Template \\
ORM & Object-Relational Mapping \\
PostgreSQL & Post-greSQL Database \\
SQL & Structured Query Language \\
UI & User Interface \\
URL & Uniform Resource Locator \\
UX & User Experience \\
\end{tabular}
\end{table}

\newpage

% Main content
\pagenumbering{arabic}
\setcounter{page}{1}

% Chapters
\include{chapter1_introduction}
\include{chapter2_literature_review}
\include{chapter3_system_analysis}
\include{chapter4_system_design}
\include{chapter5_implementation}
\include{chapter6_testing}
\include{chapter7_conclusion}

% References
\printbibliography[heading=bibintoc,title={REFERENCES}]

% Appendix
\appendix
\include{appendix}

\end{document}
